---
title: "homework_3"
output: pdf_document
date: "2025-02-10"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
```

```{r}
gasprices <- read.csv("GasPrices.csv")
library(ggplot2)
library(mosaic)
library(tidyverse)
```

# **Problem 1**

## **Part A**

There is a theory that states that gas prices could possibly charge more if there is a lack of competition in sight. This theory can be tested by comparing the gas prices and if there ar enay other gas stations in sight.

```{r}

boot_comp_prices = do(10000)*diffmean(Price ~ Competitors, data = resample(gasprices))
ggplot(data = boot_comp_prices, aes(x = diffmean)) +  
  geom_histogram(fill = "lightgoldenrod", color = "black") + labs(title = "nearby competitors vs gas prices" , x = "Difference of means of Price and competitors", y = "Count")

confint(boot_comp_prices, level = 0.95)


```

The confidence interval is between -0.055 and 0.008, with 95% confidence. This interval includes 0 meaning there isn't a significant relationship between nearby competitors and gas prices.

The theory is unsupported by this data. Since the difference of means of prices and nearby competitors includes zero it is evident that it can't be proven that gas prices charge more if they lack direct competition in sight.

## **Part B**

The theory being tested is if the richer the area, the higher the gas prices. The two factors taken into consideration are the median household income of the zip code where the gas station is located and the price of regular gasoline.

```{r}
boot_income_prices = do(10000)*{
  data <- mosaic::resample(gasprices)
  cor(data$Income , data$Price)
}

ggplot(data = boot_income_prices, aes(x = result)) +  geom_histogram(fill = "darksalmon", color = "black") + labs(title = "Income vs prices", x = "Correlation of Income and Gas prices", y = "Count")

confint(boot_income_prices, level = 0.95)

```

From just the graph you can see that majority of the correlation lies between .2 and .6. The peak is at 0.4. More specifically The correlation between gas prices and the income of the areas is somewhere between 0.198 and 0.574, with 95% confidence. Because this interval is positive, it suggests that higher average income means higher gas prices. Zero is not a part of this interval meaning there is a statistically significant correlation between the two. Because this is a sample we can't be 100% this is true. Though there is a strong relationship, we can't specifically say that the gas prices are higher purely because of the higher income in areas. 

In conclusion This theory is supported with evidence to back it up. 

\newpage

## **Part C**

The next theory being tested is if gas stations at stoplights charge more. This theory is being tested using the price of regular gas and if there is a soplight in front of the gas station. 

```{r}
boot_stop_prices = do(10000)*diffmean(Price ~ Stoplight, data = resample(gasprices))
ggplot(boot_stop_prices, aes(x= diffmean)) + geom_histogram(fill = "lightgreen", color = "black") + labs(title= "Stoplight vs gasprices", x = "Difference of mean of stoplights and gas prices", y = "Count")

confint(boot_stop_prices, level = 0.95)

```

Looking at the graph you can see that majority of the difference of mean between gas prices and if there is a stoplight is between -0.04 and 0.04. More specifically the confidence interval is somewhere between -.038 and 0.030. Because this interval includes zero there is not a statistical significance between gas prices and if there is a stoplight nearby.

We can conclude that this theory is not supported by this data. It is important to keep in mind that this is just a sample. This is between 10,000 gas stations. For these 10,000 gas stations there is not enough proof to show that the gas prices are increased depending on if there is a stoplight nearby. 

\newpage

## **Part D**

The theory being tested is if gas stations with direct highway access charge more. This theory is being tested using regular gas prices and if the gas station is accessible from either a highway or a highway access road. 
```{r}
boot_highway_prices = do(10000)*diffmean(Price ~ Highway, data = resample(gasprices))
ggplot(boot_highway_prices, aes(x= diffmean)) + geom_histogram(fill = "pink", color = "black") + labs(title= "Highway vs gasprices", x = "Difference of mean of Highway and gas prices", y = "Count")

confint(boot_highway_prices, level = 0.95)

```

Looking at the histogram it is evident that majority of the difference in mean of highway access and gas prices is between 0.02 and 0.06.More specifically the confidence interval is somewhere between .008 and 0.081, with 95% confidence. Because this interval is positive, it suggest that gas stations that are accessible from highways have higher prices than those that don't 

It can be concluded that this theory can be supported by the evidence. Because this is a sample of 10,000 there are still uncertainties. It can't be named if the higher gas prices are purely due to the fact that they accessible off a highway. This just shows a 95% confidence interval for this sample. 

\newpage

## **Part E**

The theory being tested is if Shell charges more than all other non-Shell brands. It is being tested using the regular price of gas and the brand of gas which is ExxonMobil, ChevronTexaco, Shell or other. 

```{r}
gasprices <- gasprices %>%
  mutate(brand_group = ifelse(Brand== "Shell", "Shell", "Other"))
boot_brand_prices <- do(10000)* diffmean(Price ~ brand_group, data = resample(gasprices))
ggplot(boot_brand_prices, aes(x = diffmean)) + geom_histogram(fill = "skyblue", color = "black") + labs(title = "Shell and other brands vs gas prices" , x = "Difference in means of Shell gas stations and gas prices", y = "Count")

confint(boot_brand_prices, level = 0.95)
```

Looking at the histogram it is evident that the difference in means of Shell gas stations and gas prices is between 0 and a little over .05. More specifically the confidence interval is somewhere between -0.010 and 0.066, with 95% confidence. Zero is in this interval meaning there isn't a statistical significance between Shell gas stations vs others when it comes to gas prices. 

In conclusion this theory cannot be supported by the evidence. Since this is a sample of 10,000 it means that this specific sample shows no correlation between the two.

\newpage

# **Problem 2**

```{r}
sclass <- read.csv("sclass.csv")
```

## **Part A**

```{r}
sclass_2011 <- sclass %>% filter(year == 2011, trim == "63 AMG")
boot_mileage <- do(10000)*mean(~mileage, data = resample(sclass_2011))
confint(boot_mileage, level = 0.95)

```

This shows that we are 95% confident that the true average mileage of all 2011 S-Class 63 AMG Mercedes vehicles in the population falls between 26,271.17 and 31,750.53 miles.  


## **Part B**

```{r}
sclass_2014 <- sclass %>% filter(year == 2014, trim == "550")
sclass_2014 <- sclass_2014 %>%
  mutate(isBlack = ifelse (color == "Black", yes=TRUE, no=FALSE))
boot_color <- do(10000)*prop(~isBlack, data = resample(sclass_2014))
confint(boot_color, level = 0.95)
```
Based on this we are 95% confident that the true proportion of black 2014 S-Class 550 Mercedes vehicles in the population falls between 41.68% and 45.28%. 

\newpage

# **Problem 3**

```{r}
nbc <- read.csv("nbc_pilotsurvey.csv")
```

## **Part A**

```{r}
Ed_and_Earl <- nbc %>% filter(Show == "Living with Ed" | Show == "My Name is Earl")
boot_happy <- do(10000)*diffmean(Q1_Happy ~ Show, data = resample(Ed_and_Earl))
confint(boot_happy)
```

We are trying to see if either the show Living with Ed or the show My Name is Earl makes people happier. The confidence interval of the difference in mean of people's happiness from the shows is somewhere between -.401 and 0.101. Because zero is in this interval, there is no evidence to prove that one show make people happier than the other. If the interval was positive that would have meant that My name is Earl made people happier. If it was negative that would mean Living with Ed made people happier. Since it includes zero we cannot conclude that either made people happier. 


## **Part B**

```{r}
Loser_and_Apprentice <- nbc %>% filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")
boot_annoyed <- do(10000)*diffmean(Q1_Annoyed ~ Show, data = resample(Loser_and_Apprentice))
confint(boot_annoyed)
```

We are trying to see if the show The biggest Loser or the show The Apprentice: Los Angeles make people feel more annoyed. I used bootstrapping to find the confidence interval. The confidence interval of the difference in means is somewhere between -.520 and -.019. This means that The Apprentice:Los Angeles was more annoying to people. 

## **Part C**

```{r}
Dancing_with_the_stars <- nbc %>% filter(Show == "Dancing with the Stars")
Dancing_with_the_stars <- Dancing_with_the_stars %>%
  mutate(isConfusing = ifelse(Q2_Confusing >=4, yes = TRUE, no = FALSE))
boot_confusing <- do(10000)*prop(~isConfusing, data = resample(Dancing_with_the_stars))
confint(boot_confusing)
```
The question trying to be answered is if people find Dancing with the starts confusing. I bootstrapped the data using the isConfusing variable to find confidence interval. The confidence interval is somewhere between .0387 and .116. This means that very few people are confused with the show. 

\newpage

# **Problem 4: EBay**

```{r}
ebay <- read.csv("ebay.csv")
ebay <- ebay%>%
  mutate(revenue_ratio = rev_after / rev_before)
boot_ratio <- do(10000)*diffmean(revenue_ratio ~ adwords_pause, data = resample(ebay))
confint(boot_ratio)

```

We are trying to see if advertising on Google adWords for the whole DMA is driving extra revenue. I bootsrapped the data of revenue ratio and the treatment vs control group. The confidence interval is somewhere between -0.091 and -.012. This means the treatment group is lower than the control group. It can be concluded that the advertisements are driving extra revenue. 