---
title: "Homework_8"
output: pdf_document
date: "2025-04-13"
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
```

```{r}
library(boot)
library(mosaic)
library(dplyr)
library(ggplot2)
```


```{r}
creatinine <- read.csv("creatinine.csv")
```

# **Problem 1**
## **Part A**
```{r}
model <- lm(creatclear ~ age, data = creatinine)
coeffs <- coef(model)
coeff_tibble <- tibble(
  intercept  = coeffs[1], 
  slope = coeffs[2]
)
coeff_tibble
```

The equation to find the creatinine clearance rate for a 55 year old is to take the intercept 147.813 + (slope of -.620 * 55) to get 113.723. 

## **Part B**
The creatinine clearance rate decreases by -.620 mL/minute with age. This was found by looking at the slope. 

## **Part C**
This would be done by comparing the actual clearance rate and the expected ratae for their age. The expected rates are 147.813 - 0.61982 * 40 = 123.020 for the fourty year old and 147.813 - 0.61982 * 60 = 110.624. Then you compare actual with expected by doing 135 - 123.02 = 11.98 and 112 - 110.62 = 1.38. The 40 year old has a healthier creatinine clearence rate for their age because it is about 12 mL/min higher than expected. 

# **Problem 2**
```{r}
covid <- read.csv("covid.csv")
```


```{r}
italy <- covid %>%filter(country == "Italy") %>%
  mutate(log_deaths = log(deaths))

lm_italy <- lm(log_deaths ~ days_since_first_death, data = italy)

growth_rate <- coef(lm_italy)["days_since_first_death"]

doubling_time<- 70 / (growth_rate*100)

boot_growth_rate <- do(10000) * {
  resampled_data <- resample(italy)
  model <- lm(log_deaths ~ days_since_first_death, data = resampled_data)
  growth_rate_boot <- coef(model)[2]
  data.frame(growth_rate = growth_rate_boot)
}

boot_doubling_time <- do(10000) * {
  Model1 <- lm(log(deaths) ~ days_since_first_death, data = resample(italy))
    growth_rate_boot <- coef(Model1)[2]
  data.frame(doubling = 70 / (growth_rate_boot * 100))
}
    
confint(boot_doubling_time)


confint(boot_growth_rate)


```

The estimated growth rate for Italy is .183 per day and the doubling time is 70/18.3 is approximately 3.8 days. The 95% confidence interval for the growth rate is between 0.159 and 0.209. The 95% confidence interval for the doubling time is between 3.355 and 4.416. 


## **Part 3**
```{r fig.width = 5, fig.height = 3}
ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) + geom_line(size = 1) + labs(title = "Reported daily covid deaths over time", x = "Days since firsth death", y = "Daily Deaths", color = "Country")
```


# **Problem 3**
```{r}
milk <- read.csv("milk.csv")
```


```{r}
model <- lm(log(sales) ~ log(price), data = milk)
summary(model)

boot_elasticity <- do(10000) * {
  resampled_data <- resample(milk) 
  model <- lm(log(sales) ~ log(price), data = resampled_data)
  elasticity_boot <- coef(model)[2]
  data.frame(elasticity = elasticity_boot)
}
confint(boot_elasticity)



  
```

The estimated price elasticity of demand for milk is -1.619. The log of both sales and price is taken. Then a regression model is formed that shows how the percentage change in sales relates to precentage change in price.  
