---
title: "homework_4"
output: pdf_document
date: "2025-02-18"
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )
```

```{r}
library(mosaic)
library(tidyverse)
library(knitr)
```


# **Problem 1**
```{r}
#Simulate amount of times that a trade gets flagged out of 2021 times with a probability of 2.4%. Run this simulation 100,000 times. 
flagged = do(100000)*nflip(n=2021, prob=.024)

#Find the pvalue as a proportion to the amount of times the simulation was done. 
sum_flagged = sum(flagged >= 70)/100000

#Create a histogram of the distribution
ggplot(flagged, aes(x = nflip)) + geom_histogram(fill = "lightblue", color = "black")


```

The null hypothesis is that the number of flagged trades from the Iron Bank employees is equal to the baseline rate of 2.4%. The test statistic is the observed data proportion to the expected. The p-value is `r sum_flagged`. Because this p-value is so small we would reject the null hypothesis. This means that the flagged trades are higher than the baseline rate of 2.4%.


# **Problem 2**
```{r}
#Run a simulation of if there is a health code violation out of 50 with a probability of 3%. Run this simulation 100,000 times. 
sim_health = do(100000)*nflip(n = 50, prob = .03)

#Create a histogram of the distribution
ggplot(sim_health, aes(x = nflip)) + geom_histogram(fill = "lavender", color = "black")

#Find the p-value
p_value = sum(sim_health >= 8)/100000

```


The null hypothesis is that Gourmet Bites' health code violation is the same as the average violation rate  of 3%. The test statistic is the observed number violations. The p value is `r p_value`. This p value rejects the null hypothesis meaning that Gourmet bites has a higher health code violation rate than the city average. 


# **Problem 3**
```{r}
#Set expected values for each group
expected_distribution = c(group1 = .3, group2 = .25, group3 = .2, group4 = .15, group5 = .1)

#Set observed values for each group
observed_counts = c(group1 = 85, group2 = 56, group3 = 59, group4 = 27, group5 = 13)

#Get the total number of observations
num_people = sum(observed_counts)

#Create a function that calculates the chi square statistic
chi_squared_statistic = function(observed, expected) {
  sum((observed - expected)^2 / expected)
}

#Compute chi squared for the observed data
expected_counts = num_people*expected_distribution
chi2 = chi_squared_statistic(observed_counts, expected_counts)

#Stimulate null distribution under H0
num_simulations = 10000
chi2_sim = do(num_simulations)*{
  simulated_counts = rmultinom(1, num_people, expected_distribution)
  this_chi2 = chi_squared_statistic(simulated_counts, num_people*expected_distribution)
  c(chi2 = this_chi2) 
}


p_value = sum(chi2_sim$chi2 >= chi2)/100000

```

The null hypothesis is that the racial composition of juries selected by the judge follows the same distribution as the county's eligible jury population. The test statistic I used was chi squared. The p-value is `r p_value`, which rejects the null hypothesis. This means the jury selection did not follow the county's race distribution. 



# **Problem 4**

## **Part A**
```{r}
sentences <- readLines("brown_sentences.txt")
letter_frequencies = read.csv("letter_frequencies.csv")

chi_square_stats <- sapply(sentences, function(sentence) {
  clean_sentence <- gsub("[^A-Za-z]", "", sentence)
  clean_sentence <- toupper(clean_sentence)
  
  observed_counts <- table(factor(strsplit(clean_sentence, "")[[1]], levels = LETTERS))
  total_letters <- sum(observed_counts)
  expected_counts <- total_letters * letter_frequencies$Probability
  sum((observed_counts - expected_counts)^2 / expected_counts)
})

chi_square <- data.frame(Sentence = sentences, ChiSquared = chi_square_stats)
ggplot(chi_square, aes(x = ChiSquared)) + geom_histogram(fill = "lightgreen", color = "black")+ labs(title = "Chi Square stats of the sentences", x = "ChiSquare", y = "count")

  


```

## **Part B**


```{r}
sentences <- c(
  "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
  "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
  "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
  "He carefully examined the document, looking for any clues that might help solve the mystery.",
  "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
  "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
  "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
  "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
  "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
  "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)


compute_chi_square <- function(sentence, letter_frequencies){
  clean_sentence <- gsub("[^A-Za-z]", "", sentence)
  clean_sentence <- toupper(clean_sentence)
  
  observed_counts <- table(factor(strsplit(clean_sentence, "")[[1]], levels = LETTERS))
  total_letters <- sum(observed_counts)
  expected_counts <- total_letters * letter_frequencies$Probability
  chi_sq_value <- sum((observed_counts - expected_counts)^2 / expected_counts)
  
  return(chi_sq_value)
  
}
results <- data.frame(Sentence = sentences, ChiSquared = NA, PValue = NA)

for(i in seq_along(sentences)){
  chi_sq_value <- compute_chi_square(sentences[i], letter_frequencies)
  
  p_value <- mean(chi_square_stats >= chi_sq_value, na.rm = TRUE)
  
  results$ChiSquared[i] <- chi_sq_value
  results$PValue[i] <- p_value
}

results$PValue <- round(results$PValue, 3)
results$Sentence <- paste("Sentence", seq_len(nrow(results)))
kable(results, col.names = c("Sentences", "Chi-Squared","P-Value"))
```



The sentence generated by an LLM is the sixth sentence. This is because the Chi Squared is significantly higher and the p-value is significantly lower than all the others. 

